Atmospheric escape and star-planet-interaction in the HAT-P-67 b system

### 2023-02-07 paper/paper1/ms.tex
Re-reading and fixing the analysis section

Candidates for detection should be observable in one of three atomic lines.  Ly~$\alpha$, \ion{He}{1} 10833 \AA, and H~$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2023MNRAS.518.4357O}.  Ly $\alpha$ can exhibit strong atmospheric escape signals, but instellar medium \ion{H}{1} absorption censors its low-velocity linecore.  \ion{He}{1} 10833 \AA offers significant advantages over Ly~$\alpha$, and has resulted in 8 systems with detections to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.  These detections exhibit a range of signal strengths, as high as 10$\%$ transit depths.  Measurements at high spectral resolution have been especially valuable for evincing velocity substructure of the escaping gas motion relative to the exoplanet restframe \citep{2019A&A...629A.110A,2020ApJ...894...97N}, and convincingly associating the signal to an exoplanetary origin as opposed to stellar contamination \citep{2018AJ....156..189C}.

@@

The Habitable Zone Planet Finder Spectrograph \citep[HPF][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET][]{1998SPIE.3352...34R} operates in the near-IR from $8100-12800~\AA\;$ spanning the \textit{z}, \textit{Y}, and \textit{J} bands at spectral resolving power $R=55,000$. The HET fixed-elevation design \citep{2007PASP..119..556S} limits the observability of HAT-P-67 to less than 1 hour ``tracks'' for a fixed range of hour angles before (east track) and after (west track) transiting the meridian.  Whereas conventional steerable telescopes could conduct cintinuous point-and-stare observations of HAT-P-67 for hours, HET cannot.  In practice, this limitation means that in-transit and out-of-transit were rarely possible on the same night.  Instead, we organized the observations into four campaigns to coincide with HAT-P-67b transits on the nights beginning 2020 April 28, 2020 May 22, 2020 June 15, and 2022 April 28.  These in-transit nights had up to 14 exposures per HET track, with integration times between 5-8.5 minutes.  We obtained out-of-transit baseline observations up to 2 nights before and after the transit, plus random-in-phase low priority P4 queue-filler observations.  These out-of-transit observations typically received 4 or fewer individual exposures.  We observed HAT-P-67 with HPF for a total 41 visits on 39 unique nights, with two of those nights observing both an east and a west track.  The total on-source integration time exceeds 13.8 hours.  Table \ref{tabHPFLog} summarizes the log of observations.

The observation scheduling was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature.  The small BERV still means the redward Helium linewing has significant telluric contamination between 10834-10836$\AA$, but the core and blue line wings appear relatively pristine.

@@

\subsection{Other archives}
We searched for observations of HAT-P-67 in public archives.  It has one $R\sim8000$ spectrum from the Intermediate Dispersion Spectrograph on the INT, centered near 4000 $\AA$.  It has 26 photometry points from \emph{Pan-STARRS} spread across its 5 filters.  The other archival observations have been previously reported by \citet{2017AJ....153..211Z}, including Keck HIRES, Keck NIRC2, and WIYN High-Resolution Infrared Camera.  The northern source does not appear in ESO archives, nor the Gemini Archive, and it is not publicly accessible in the Zwicky Transient Factory (ZTF) archive.  It was not targeted by Spitzer or Hubble.

@@

\subsubsection{Revised exoplanet orbital parameters}
We assembled a composite lightcurve by stitching TESS Sectors 24, 26, 51, 52, 53, which were reduced with the default SPOC pipeline \citep{2020RNAAS...4..201C}, and lightly post-processed with \texttt{lightkurve} \citep{geert_barentsen_2019_2565212}.  These TESS data exhibit an RMS scatter of better than 1 part-per-thousand (ppt) at native 2-minute sampling.  We fit a Keplerian orbit model to the TESS lightcurve using the \texttt{exoplanet} framework \citep{exoplanet:joss}.  We obtained a best fit orbital period of $4.81011$ days, non-zero eccentricity of 0.19, an impact parameter of 0.46, planet-to-star radius of 0.0823, transit depth of 0.74\%, and $T_0$ of 1958.07933 in BTJD.  These properties are consistent with the previously reported values from \citet{2017AJ....153..211Z}.  Figure \ref{fig:transit} shows the best-fit orbit overlaid on the detrended TESS lightcurve.  Table \ref{tabOrbit} lists one of the previous orbit determinations and solution reported here.

@@

If we attribute the TESS modulation signal to stellar activity, we obtain a rotation period $P_\mathrm{rot}$ between 4.7 and 5.9 days.  \citet{2017AJ....153..211Z} estimated $v\sin{i}=35.8\pm1.1$ km/s, or lower ($v\sin{i}=30\pm1.1$ km/s) if macroturbulence was accounted for.  We obtain a combined geometric constraint $2.85< R_\star \sin{i} (R_\odot) < 4.2 $.  The lower end of these constraints are consistent with  the 1-$\sigma$ range of $2.0 < R_\star (R_\odot) < 3.2$ provided in \citet{2017AJ....153..211Z} from different isochrones and orbit fits, and assuming a near-edge-on orbital inclination.  The Gaia \emph{DR3}-derived distance is 8\% greater than the \emph{Gaia} DR1 estimate used in \citet{2017AJ....153..211Z}; the revised larger distance would tend to increase the radius estimate by 16\% to match the observed SED in isochrone-fitting.  We would therefore expect an isochrone-deived $R_\star$ range closer to $2.5-3.14 R_\odot$, where we have dropped the 1-$\sigma$ uncertainties which had included the less certain Gaia DR 1 parallax and its uncertain correction terms.  For a fixed $R_p/R_\star$, the larger $R_\star$ implies a proportionally larger planet radius, revising the already-low density of HAT-P-67 even lower.

@@

\begin{deluxetable*}{lrrrh}
    \tablewidth{0pc}
    \tabletypesize{\scriptsize}
    \tablecaption{
        Revised orbital and planetary parameters
        \label{tabOrbit}
    }
    \tablehead{
        \colhead{Parameter}   &
        \colhead{Zhou et al. 2017} &
        \colhead{Ivshina \& Winn 2022} &
        \colhead{This Work} &
        \nocolhead{Alternate}
    }
    \startdata
    %%
    ~~~$P$ (days)             \dotfill    & $4.8101025_{-3.3\times 10^{-7}}^{+4.3\times 10^{-7}}$ & 4.8101046$\pm1.7\times10^{-6}$ & 4.81011 & z \\
    ~~~$T_c$ (${\rm BTJD}$)  \dotfill    & $-1038.61533_{-0.00064}^{+0.00076}$ & 1958.08059$\pm$0.00032 & 1958.07933 & z \\
    ~~~$T_{14}$ (hours)  \dotfill    & $6.9888 \pm 0.046$ &  & 7.0636 & z \\
    ~~~$T_{12} = T_{34}$ (days)  \dotfill    & $0.0229\pm0.0010$ &  &  & z \\
    ~~~$\arstar$              \dotfill    & $5.691_{-0.124}^{+0.057}$ &  &  & z \\
    ~~~$\rpl/\rstar$          \dotfill    & $0.0834\pm0.0017$ &  & 0.08231 & z \\
    ~~~$b \equiv a \cos i/\rstar$
    \dotfill    & $0.12_{-0.08}^{+0.12}$ &  & 0.45616 & z \\
    ~~~$i$ (deg)              \dotfill    & $88.8_{-1.3}^{+1.1}$ &  &  & z \\
    \enddata
\end{deluxetable*}

\subsection{HPF analysis}
Ideally we seek the pixel-to-pixel substructured spectrum of the helium exosphere, corrected for all the conceivable instrumental, telluric, and stellar contamination artifacts.  In practice, these corrections are incomplete.  We experimented with a range of pre-processing and analysis techniques to quantify the accuracy and precision of our HPF spectra.

The raw 2D echellograms were reduced with the \texttt{Goldilocks} package\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}}, which outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb (LFC).  The observations were acquired with the LFC turned off, so this unilluminated spectrum was discarded.

@@

We masked spectral regions predicted to have significant telluric lines with a template generated by \texttt{telfit} \citep{2014AJ....148...53G}.  We shifted the spectral coordinates to their common barycentric-corrected reference frame \citep{2014PASP..126..838W} as implemented in \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A}.  We flattened the spectra to two pre-selected continuum indices highlighted as vertical blue bands in Figure \ref{fig:HPFheliumOverview}.  The sky-subtraction, telluric masking, barycentric correction, flattening, and all of our other standard pre-processing steps were carried out in the open-source Python interface \texttt{muler} \citep{2022JOSS....7.4302G}.

Figure \ref{fig:HPFheliumOverview} shows a zoom-in on the He 10830 region of interest, with all 153 individual exposures overlaid.  We see a variability in the Helium line of up to 10\%, much greater than the $<1\%$ pixel-to-pixel variation.  The feature width spans about 3 $\AA~$, comparable to the stellar rotationally lines too broad to originate from the much narrower telluric lines.

\begin{figure}
    \includegraphics[width=\linewidth]{figures/HAT_P_67b_He_spectrum.png}
    \caption{Overlay of all 128 individual HPF exposures of HAT-P-67, spanning 2020-2022. Variability is seen in the Helium 10833 $\AA$ band, denoted by the vertical orange shaded band, but not in the adjacent regions.  These snapshot spectra were barycentric corrected, and continuum flattened to the regions in the blue vertical bands.  Sharp telluric absorption lines have been masked in regions near 10835 and 10837.5 $\AA$.}
    \label{fig:HPFheliumOverview}
\end{figure}

The 13.8 hours of exposure, combined with HAT-P-67b's short ($P\sim4.8$ day) period, means that a large fraction of the orbit has been collected, with some phases (especially near transit) heavily sampled, and some other out-of-transit phases sampled only sparsely. We constructed a 2-D intensity phase scan, binning in phase and wavelength, and spanning the entire orbit of HAT-P-67.  Figure \ref{fig:HPFphase2D} overlays the planet's approximately $\pm150\;$km/s orbital Doppler velocity, with the stellar rest frame velocity demarcated by the vertical line.  The vanishing $<36$ m/s reflex motion of the star is imperceptible at this scale.  The horizontal dashed lines indicate the transit ingress, midcenter, and egress.

\begin{figure}
    \includegraphics[width=\linewidth]{figures/phase_2D_diagram.png}
    \caption{Phase scan of intensity for HAT-P-67.  The spectrum flux intensity shows significant in-transit absorption during and before the transit.  Telluric lines redward of the line center have been masked.  An unmasked telluric line near 10825 $\AA$ can be seen.}
    \label{fig:HPFphase2D}
\end{figure}

A large absorption signal can be seen preceding transit ingress, with some significant absorption evident before $-0.2$ in phase.  We construct a fractional residual absorption spectrum by subtracting off and re-normalizing to the non-varying baseline.  We define the non-varying baseline spectrum as the average over phases $0.3-0.5$, which exhibited stable spectra with the lease absorption.  Figure \ref{fig:HPFscanResid} shows a conspicuous view of the Helium absorption of HAT-P-67b.  Significant absorption can be seen as a few percent at $-0.37$ in phase, rising to 10\% just before and during transit.  The egress drop off is extremely sharp, with almost no absorption directly after transit.

The absorption resides mostly near the stellar zero restframe velocity reference.  As mentioned previously, the telluric masking near 10836 $\AA$ censors our view of the existence (or not) of any redshifted lobe in this region.  A more careful treatment of the telluric absorption could rescue some of the data in this region.

@@

\subsection{Calcium IR Triplet and other line diagnostics}
We examined the Calcium IR Triplet lines (Ca IRT) for evidence of variability.  No variation was seen in these features, which were pre-processed in the same way as the Helium feature.  Figure \ref{fig:CaPhaseScan} shows a similar phase plot as Figure \ref{fig:HPFscanResid}, adapted to the line at 8662 $\AA$.  We see no conspicuous variability at this or any of the other Ca IRT lines.  We also found no detectable variability in the Pa$\delta$ line at 10050 $\AA$, nor other deep lines at 10330 $\AA$ and elsewhere.  Helium 10830 appears to be the only conspicuously variable line in the HPF spectrum.

>>>>

Candidates for detection should be observable in one of three atomic lines.  Ly~$\alpha$, \ion{He}{1} 10833 \AA, and H~$\alpha$ have emerged as the most amenable to detection \citep{2018ApJ...855L..11O,2023MNRAS.518.4357O}.  Ly $\alpha$ can exhibit strong atmospheric escape signals, but instellar medium \ion{H}{1} absorption censors its low-velocity linecore.  \ion{He}{1} 10833 \AA~ offers significant advantages over Ly~$\alpha$, and has resulted in 8 systems with detections to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.  These detections exhibit a range of signal strengths, as high as 10$\%$ transit depths.  Measurements at high spectral resolution have been especially valuable for evincing velocity substructure of the escaping gas motion relative to the exoplanet restframe \citep{2019A&A...629A.110A,2020ApJ...894...97N}, and convincingly associating the signal to an exoplanetary origin as opposed to stellar contamination \citep{2018AJ....156..189C}.

@@

The Habitable Zone Planet Finder Spectrograph \citep[HPF;][]{2012SPIE.8446E..1SM,2014SPIE.9147E..1GM, 2019Optic...6..233M} on the queue-scheduled 10-meter \emph{Hobby-Eberly Telescope} \citep[HET;][]{1998SPIE.3352...34R} operates in the near-IR from $8100-12800~$\AA~ spanning the \textit{z}, \textit{Y}, and \textit{J} bands at spectral resolving power $R=55,000$. The HET fixed-elevation design \citep{2007PASP..119..556S} limits the observability of \object{HAT-P-67} to less than 1 hour ``tracks'' for a fixed range of hour angles before (east track) and after (west track) the star transits the meridian.  Whereas conventional steerable telescopes could conduct continuous point-and-stare observations of \object{HAT-P-67} for hours, HET cannot.  In practice, this limitation means that in-transit and out-of-transit observational phases were rarely possible on the same night.  Instead, we organized the observations into four campaigns to coincide with \object{HAT-P-67 b} transits on the nights beginning 2020 April 28, 2020 May 22, 2020 June 15, and 2022 April 28.  These in-transit nights had up to 14 exposures per HET track, with integration times between 5-8.5 minutes.  We obtained out-of-transit baseline observations up to 2 nights before and after the transit, plus random-in-phase low priority P4 queue-filler observations.  These out-of-transit observations typically received 4 or fewer individual exposures.  We observed HAT-P-67 with HPF for a total 41 visits on 39 unique nights, with two of those nights observing both an east and a west track.  The total on-source integration time exceeds 13.8 hours.  Table \ref{tabHPFLog} summarizes the log of observations.

The observation scheduling was strategically restricted to the spring season when the Barycentric Earth Radial Velocity (BERV) would Doppler shift telluric absorption lines sufficiently far away from the core of the Helium 10833$\AA~$ feature.  The small BERV still means the redward Helium linewing has significant telluric contamination between 10834-10836 \AA, but the core and blue line wings appear relatively pristine.

@@

\subsection{Other archives}
We searched for observations of HAT-P-67 in public archives.  It has one $R\sim8000$ spectrum from the Intermediate Dispersion Spectrograph on the INT, centered near 4000 \AA.  It has 26 photometry points from \emph{Pan-STARRS} spread across its 5 filters.  The other archival observations have been previously reported by \citet{2017AJ....153..211Z}, including Keck HIRES, Keck NIRC2, and WIYN High-Resolution Infrared Camera.  The northern source does not appear in ESO archives, nor the Gemini Archive, and it is not publicly accessible in the Zwicky Transient Factory (ZTF) archive.  It was not targeted by \emph{Spitzer} or \emph{Hubble}.

@@

\subsubsection{Revised exoplanet orbital parameters}
We assembled a composite lightcurve by stitching TESS Sectors 24, 26, 51, 52, 53, which were reduced with the default SPOC pipeline \citep{2020RNAAS...4..201C}, and lightly post-processed with \texttt{lightkurve} \citep{geert_barentsen_2019_2565212}.  These TESS data exhibit an RMS scatter of better than 1 part-per-thousand (ppt) at native 2-minute sampling.  We fit a Keplerian orbit model to the TESS lightcurve using the \texttt{exoplanet} framework \citep{exoplanet:joss}.  We obtained a best fit orbital period of $4.81011$ days, non-zero eccentricity of 0.19, an impact parameter of 0.46, planet-to-star radius ratio of 0.0823, transit depth of 0.74\%, and $T_0$ of 1958.07933 in BTJD.  These properties are consistent with the previously reported values from \citet{2017AJ....153..211Z} and the updated ephemeris of \citet{2022ApJS..259...62I}.  Figure \ref{fig:transit} shows the best-fit orbit overlaid on the detrended TESS lightcurve.  Table \ref{tabOrbit} lists one of the previous orbit determinations and solution reported here.

@@

If we attribute the TESS modulation signal to stellar activity, we obtain a rotation period $P_\mathrm{rot}$ between 4.7 and 5.9 days.  \citet{2017AJ....153..211Z} estimated $v\sin{i}=35.8\pm1.1$ km/s, or lower ($v\sin{i}=30\pm1.1$ km/s) if macroturbulence was accounted for.  We obtain a combined geometric constraint $2.85< R_\star \sin{i}  < 4.2 $ in units of $R_\odot$.  The lower end of these constraints is consistent with  the 1-$\sigma$ range of $2.0 < R_\star < 3.2$ provided in \citet{2017AJ....153..211Z} from different isochrones and orbit fits, and assuming a near-equator-on orbital inclination.  The Gaia \emph{DR3}-derived distance is 8\% greater than the \emph{Gaia} DR1 estimate used in \citet{2017AJ....153..211Z}; the revised larger distance would tend to increase the radius estimate by 16\% to match the observed SED in isochrone-fitting.  We would therefore expect an isochrone-derived $R_\star$ range closer to $2.5-3.14 R_\odot$, where we have dropped the 1-$\sigma$ uncertainties which had included the less certain Gaia DR 1 parallax and its uncertain correction terms.  For a fixed $R_p/R_\star$, the larger $R_\star$ implies a proportionally larger planet radius, revising the already-low density of HAT-P-67 even lower.

@@

\begin{deluxetable*}{lrrrh}
    \tablewidth{0pc}
    \tabletypesize{\scriptsize}
    \tablecaption{
        Revised orbital and planetary parameters
        \label{tabOrbit}
    }
    \tablehead{
        \colhead{Parameter}   &
        \colhead{Zhou et al. 2017} &
        \colhead{Ivshina \& Winn 2022} &
        \colhead{This Work} &
        \nocolhead{Alternate}
    }
    \startdata
    %%
    ~~~$P$ (days)             \dotfill    & $4.8101025_{-3.3\times 10^{-7}}^{+4.3\times 10^{-7}}$ & 4.8101046$\pm1.7\times10^{-6}$ & 4.81011 & z \\
    ~~~$T_c$ (${\rm BTJD}$)  \dotfill    & $-1038.61533_{-0.00064}^{+0.00076}$ & 1958.08059$\pm$0.00032 & 1958.07933 & z \\
    ~~~$T_{14}$ (hours)  \dotfill    & $6.9888 \pm 0.046$ &  & 7.0636 & z \\
    %~~~$T_{12} = T_{34}$ (days)  \dotfill    & $0.0229\pm0.0010$ &  &  & z \\
    %~~~$\arstar$              \dotfill    & $5.691_{-0.124}^{+0.057}$ &  &  & z \\
    ~~~$\rpl/\rstar$          \dotfill    & $0.0834\pm0.0017$ &  & 0.08231 & z \\
    ~~~$b \equiv a \cos i/\rstar$
    \dotfill    & $0.12_{-0.08}^{+0.12}$ &  & 0.45616 & z \\
    %~~~$i$ (deg)              \dotfill    & $88.8_{-1.3}^{+1.1}$ &  &  & z \\
    \enddata
\end{deluxetable*}

\subsection{HPF analysis}
The raw 2D echellograms were reduced with the \texttt{Goldilocks} package\footnote{\url{https://github.com/grzeimann/Goldilocks_Documentation}}, which outputs 1D extracted spectra for the target, and two reference fibers: blank sky and a laser frequency comb (LFC).  The observations were acquired with the LFC turned off, so this unilluminated spectrum was discarded.

@@

We masked spectral regions predicted to have significant telluric lines with a template generated by \texttt{telfit} \citep{2014AJ....148...53G}.  We shifted the spectral coordinates to their common barycentric-corrected reference frame \citep{2014PASP..126..838W} as implemented in \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A,2022ApJ...935..167A}.  We flattened the spectra to two pre-selected continuum indices highlighted as vertical blue bands in Figure \ref{fig:HPFheliumOverview}.  The sky-subtraction, telluric masking, barycentric correction, flattening, and all of our other standard pre-processing steps were carried out in the open-source Python interface \texttt{muler} \citep{2022JOSS....7.4302G}.

Figure \ref{fig:HPFheliumOverview} shows a zoom-in on the He 10830 region of interest, with all 153 individual exposures overlaid.  We see a variability in the Helium line of up to 10\%, much greater than the $<1\%$ pixel-to-pixel variation.  The feature width spans about 3~\AA, comparable to the stellar rotationally broadened lines and too broad to originate from the much narrower telluric lines.

\begin{figure}
    \includegraphics[width=\linewidth]{figures/HAT_P_67b_He_spectrum.png}
    \caption{Overlay of all 128 individual HPF exposures of HAT-P-67, spanning 2020-2022. Variability is seen in the \ion{He}{1} 10833 \AA~ triplet, denoted by the vertical orange shaded band, but not in the adjacent regions.  These snapshot spectra were barycentric corrected, and continuum flattened to the regions in the blue vertical bands.  Sharp telluric absorption lines have been masked in regions near 10835 and 10837.5 $\AA$.}
    \label{fig:HPFheliumOverview}
\end{figure}

The 13.8 hours of exposure, combined with \object{HAT-P-67 b}'s short ($P\sim4.8$ day) period, means that a large fraction of the orbit has been collected, with some phases (especially near transit) heavily sampled, and some other out-of-transit phases sampled only sparsely. We constructed a 2-D intensity phase scan, binning in phase and wavelength, and spanning the entire orbit of \object{HAT-P-67 b}.  Figure \ref{fig:HPFphase2D} overlays the planet's approximately $\pm150\;$km/s orbital Doppler velocity, with the stellar rest frame velocity demarcated by the vertical line.  The vanishing $<36$ m/s reflex motion of the star is imperceptible at this scale.  The horizontal dashed lines indicate the transit ingress, midcenter, and egress.

\begin{figure}
    \includegraphics[width=0.8\linewidth]{figures/phase_2D_diagram.png}
    \caption{Phase scan of intensity for HAT-P-67.  The spectrum flux intensity shows significant in-transit absorption during and before the transit.  Telluric lines redward of the line center have been masked.  An unmasked telluric line near 10825 \AA~ can be seen.}
    \label{fig:HPFphase2D}
\end{figure}

A large absorption signal can be seen preceding transit ingress, with some significant absorption evident before $-0.2$ in phase.  We construct a fractional residual absorption spectrum by subtracting off and re-normalizing to the non-varying baseline.  We define the non-varying baseline spectrum as the average over phases $0.3-0.5$, which exhibited stable spectra with the least absorption.  Figure \ref{fig:HPFscanResid} shows a conspicuous view of the Helium absorption of \object{HAT-P-67 b}.  Significant absorption can be seen as a few percent at $-0.37$ in phase, rising to 10\% just before and during transit.  The egress drop off is extremely sharp, with almost no absorption directly after transit.

The absorption resides mostly near the stellar zero restframe velocity reference.  As mentioned previously, the telluric masking near 10836 \AA~ censors our view of the existence (or not) of any redshifted lobe in this region.  A more careful treatment of the telluric absorption could rescue some of the data in this region.

@@

\subsection{Calcium IR Triplet and other line diagnostics}
We examined the \ion{Ca}{2} IR Triplet lines (Ca IRT) for evidence of variability.  No variation was seen in these features, which were pre-processed in the same way as the Helium feature.  Figure \ref{fig:CaPhaseScan} shows a similar phase plot as Figure \ref{fig:HPFscanResid}, adapted to the line at 8662 \AA.  We see no conspicuous variability at this or any of the other Ca IRT lines.  We also found no detectable variability in the Pa$\delta$ line at 10050 \AA, nor other deep lines at 10330 \AA and elsewhere.  \ion{He}{1} 10833 appears to be the only conspicuously variable line in the HPF spectrum.
